\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\norm}[1]{\lVert#1\rVert}
\newcommand{\eqncaption}[1]{\begin{center}{\footnotesize{#1}}\end{center}\vspace{15pt}}
\newcommand{\eqnlongcaption}[1]{{\footnotesize{#1}}\vspace{15pt}}

\begin{document}

\title{Angle vs. Time vs. Strength vs. Mobility: Pros and Cons of different features for location verification}

%% author names commented out for initial release, might be needed later %%
%\author{
%    \IEEEauthorblockN{Somaye Hoseinpur}
%    \IEEEauthorblockA{\textit{Dept. of Computer Science} \\
%    \textit{University of Kaiserslautern}\\
%    Kaiserslautern, Germany \\
%    s\_hoseinpu19@cs.uni-kl.de}
%    \and
%    \IEEEauthorblockN{Sai Srinivas Jeevanandam}
%    \IEEEauthorblockA{\textit{Dept. of Computer Science} \\
%    \textit{University of Kaiserslautern}\\
%    Kaiserslautern, Germany \\
%    s\_jeevanan19@cs.uni-kl.de}
%    \and
%    \IEEEauthorblockN{Gabriele Monaco}
%    \IEEEauthorblockA{\textit{Dept. of Electronic and Information Technology} \\
%    \textit{University of Kaiserslautern}\\
%    Kaiserslautern, Germany \\
%    monaco@rhrk.uni-kl.de}
%}

\maketitle

\begin{abstract}
    Many applications are relying on location for various purposes in their activity, in general users need to advertise their own position to the server and can then spoof it. This can be dangerous in many contexts, from secure networks to aircraft. In this paper we are going to discuss about how to securely verify the location in wireless networks by exploiting physical properties of the incoming signals. It is indeed possible to determine, based on some measured parameters, if a location claim can be trustworthy and there are several methods how to do that. We are going through some of the physical properties that can be exploited for this purpose, pointing out advantages and disadvantages of the various approaches.
\end{abstract}

\section{Introduction}
Throughout this paper, we are going to discuss models in which a user needs to communicate its location to to the service handlers. We will refer as the former as \emph{prover}, since its job is to \emph{prove} its location, while the latter will be referred as \emph{verifier}, whose job is basically to check the prover's location. If not differently specified, all the communication happen in a wireless network, where the opponents can exchange radio messages.

In the next sections we will analyse separately each physical property: received angle, time of reception, signal strength, etc. For each of them we will point out strengths and weaknesses of the approach, to make clear in which application may them be effectively used and when they might not be a good option.

\section{Angle}
\input{angle}

\section{Time}
\input{time}

\section{Strength}
\input{strength}

\section{Mobility}
\input{mobility}

\section{Conclusion}
In this article, we gave a general overview of the different location verification techniques. These mechanisms have been an important subject for conducting study and research for positioning systems. However, they have to be considered from different aspects specially security. Because they can be used in applications such as IoT and any systems that require positioning objects. So improving these techniques will result in better positioning. We studied and analyzed the advantages and disadvantages of these techniques. To come to a conclusion, considering the project for positioning systems one of these techniques of mixed of them can be used. 
As mentioned before, RSS based location verification systems have many problems. These systems when combined with time difference of arrival (TDOA) perform better. Both ToA and TDoA systems are widely used for to get location in the navigation systems. However, as mentioned before an attacker could easily detect the position of a node in the ToA network, so it is recommended to obtain TDoA technique.Considering the big geolocation systems, two factors seem to be more important which are security and accuracy. Although AoA based localization techniques are not widely implemented they can be used to increase accuracy and improve verification by using along with other features. Right now even tough RSS based systems provide good enough solutions to many present applications there are limitations, challenging requirements which needs to be addressed.
In developing positioning systems, the Prioritization should be considered. As in some systems less accuracy leads to undesirable results and similarly some systems prefer the higher security. Therefore, choosing between two techniques needs to know the preferences first. All in all, four mechanisms can be compared in many aspects but depending on the application area, one technique can be chosen. Nevertheless, by advancing the technology it is expected that these techniques or even a brand new technique could be developed that has a better security and precision.

\begin{thebibliography}{00}

\bibitem{angulation} ANGULATION. http://kom.aau.dk/group/10gr891/methods/Triangulation/Angulation/ANGULATION.pdf/ [Accessed: January 2020]
\bibitem{abdelaziz19} A. Abdelaziz, R. Burton, F. Barickman, J. Martin, J. Weston and C. E. Koksal, "Enhanced Authentication Based on Angle of Signal Arrivals," in IEEE Transactions on Vehicular Technology, vol. 68, no. 5, pp. 4602-4614, May 2019.
\bibitem{wielandt17} Wielandt, S.; Strycker, L.D. Indoor Multipath Assisted Angle of Arrival Localization. Sensors 2017, 17, 2522.
\bibitem{schaefer15} M. Schäfer, V. Lenders and J. Schmitt ``Secure Track Verification,'' 2015 IEEE Symposium on Security and Privacy, San Jose, CA, pp. 199-213, 2015.
\bibitem{schaefer16} M. Schäfer, P. Leu, V. Lenders and J. Schmitt ``Secure Motion Verification using the Doppler Effect,'' Proceedings of the 9th ACM Conference on Security \& Privacy in Wireless and Mobile Networks, pp. 135-145, 2016.
\bibitem{ghose15} N. Ghose and L. Lazos ``Verifying ADS-B navigation information through Doppler shift measurements,'' 2015 IEEE/AIAA 34th Digital Avionics Systems Conference (DASC), pp. 4A2-1, 2015.
\bibitem{costin12} A. Costin and A. Francillon ``Ghost in the Air (Traffic): On insecurity of ADS-B protocol and practical attacks on ADS-B devices,'' Black Hat USA, pp.1-12, 2012.
\bibitem{brian17}B. Keefe ``Finding Location with Time of Arrival and Time Difference of Arrival Techniques.'' ECE Senior Capstone Project (2017).
\bibitem{jin18}Jin, Bonan, Xiaosu Xu, and Tao Zhang. ``Robust time-difference-of-arrival (TDOA) localization using weighted least squares with cone tangent plane constraint.'' Sensors 18.3 (2018): 778.
\bibitem{schaefer18}M. Schaefer ``Mobility Improves the Security of Location Awareness in Wireless Networks.'' (2018).
\bibitem{gante13}D. Gante, Alejandro, M. Siller. ``A survey of hybrid schemes for location estimation in wireless sensor networks.'' Procedia Technology 7 (2013): 377-383.
\bibitem{adsb}ADS-B Info. https://www.ads-binfo.com/. [Accessed: January 2020]
\bibitem{dopplersrc}INSIGHT. https://www.insightsonindia.com/2016/03/01/insights-daily-current-events-01-march-2016/ [Accessed: January 2020]
\bibitem{srivastava}R. Kasper, M. Srivastava. ``Secure location verification with hidden and mobile base stations.'' IEEE Transactions on Mobile Computing 7.4 (2008): 470-483.
\bibitem{yan14} S. Yan, R. Malaney, I. Nevat and G. W. Peters, "Signal strength based wireless Location Verification under spatially correlated shadowing," 2014 IEEE International Conference on Communications (ICC), Sydney, NSW, 2014, pp. 2617-2623.
\bibitem{pu11} Pu, Chuan Chin \& Pu, Chuan-Hsian \& Lee, Hoon-Jae. (2011). Indoor Location Tracking Using Received Signal Strength Indicator. 10.5772/10518. 
\bibitem{chenbook} Yingying Chen, Jie Yang, Chapter 8 - Defending Against Identity-Based Attacks in Wireless Networks, Handbook on Securing Cyber-Physical Critical Infrastructure, Morgan Kaufmann,2012, Pages 191-222

\end{thebibliography}

\end{document}
